Mechanized Reasoning about a Capability Machine

### 2019-10-17 prisc-2020/paper.tex
fixing authors
notes added

@@

\section{The Program Logic of a Capability Machine}
In order to give a logical account of the logical relation, we must first define a program logic for the capability machine language. Iris is a separation logic framework, which means we can embed any language into Iris by describing its small step semantics. However, the framework was designed with high level languages in mind. Embedding a language requires a definition of the expressions, the values, the state and the small step semantics.

>>>>

\author{Alix Trieu}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  %\position{Position2a}
  %\department{Department2a}             %% \department is recommended
  \institution{Aarhus University}           %% \institution is required
  %\streetaddress{Street2a Address2a}
  %\city{City2a}
  %\state{State2a}
  %\postcode{Post-Code2a}
  %\country{Denmark}                   %% \country is recommended
}
\email{alix.trieu@cs.au.dk}         %% \email is recommended

@@

\section{The Program Logic of a Capability Machine}

\begin{itemize}
\item we define the operational semantics of the CM
\item we prove basic hoare triples for each of the atomic instructions
  of the CM (i.e., for load, store, etc.)
\item non-trivial
  \begin{itemize}
  \item while Iris is a framework and supports many languages, it is
    geared towards models of higher-level languages which abstract from
    program counters and the fact that programs are stored in memory.
    -- here our low-level machine model includes registers, in particular
    the program counter register, and instructions are stored in memory.
   \item hence we 
  \end{itemize}
\end{itemize}

In order to give a logical account of the logical relation, we must first define a program logic for the capability machine language. Iris is a separation logic framework, which means we can embed any language into Iris by describing its small step semantics. However, the framework was designed with high level languages in mind. Embedding a language requires a definition of the expressions, the values, the state and the small step semantics.
